On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-08-11 Manuscript/manuscript.tex
Added info about the size of each cluster size

\begin{figure}[tbp]
  \centering
  \includegraphics{Finals_Pooled_Boxplot}
  \caption{The reaction times from 1999 to 2022 for the men's final (top) and
  the men's semifinals and finals (bottom).}
  \label{fig:Boxplots}
\end{figure}

@@

\subsubsection{2022 National Competitions}\label{sec:datanational}
From June 23-26 2022, the United States held its Track and Field Championships 
at Hayward Field in Eugene, Oregon to decide who to send to the World 
Championships being held at the same venue in August. Thus, we can establish a 
baseline for the four United States athletes who competed in at least one round 
of both events: Trey Cunningham, Daniel Roberts, 
Grant Holloway, and Devon Allen. Table~\ref{fig:USAvsWorld} highlights the 
difference in reaction times for these four athletes in the two events. 
Every athlete reacted faster in all the World 
Track and Field Championships races compared to the United States Track and Field 
Championships races. Devon Allen raced three times at the United States Track and
Field Championships and three times at the World Track and Field Championships. 
His reaction times were substantially faster in the World Track and
Field Championships compared to the United States Track and Field Championships, 
as were his teammates. 
This comparison suggests that the timing system used between the two
meets may have been meaningfully different to the point where Devon Allen was
disqualified more because of faulty equipment rather than because he reacted
too quickly.

\begin{table}
\begin{center}
  \caption{Reaction times (in seconds) for four United States Athletes at the 
	2022 United States Track
  and Field World Championships (``United States") and the 2022 World Track and Field 
	Championships (``World"); H denotes preliminary heat, S denotes semifinal, and 
	F denotes final.
  ``N/A" was used for any athlete that did not compete and thus did not register 
  a reaction time. }
  \begin{tabular}{c c c c c c c} 
   \toprule
	 & \multicolumn{3}{c}{United States} & \multicolumn{3}{c}{World} \\
	\cmidrule(lr){2-4}
    \cmidrule(lr){5-7}
   Athlete &  H &  S &  F &  H &  S &  F \\ [0.5ex] 
   \midrule
   Devon Allen & 0.201 & 0.153 & 0.160 & 0.123 & 0.101 & 0.099 \\ 
   Trey Cunningham & 0.186 & 0.185 & 0.182 & 0.115 & 0.120 & 0.109 \\
   Grant Holloway & 0.192 & 0.190 & N/A & 0.147 & 0.128 & 0.124 \\
   Daniel Roberts & 0.181 & 0.200 & 0.183 & 0.179 & N/A & N/A \\ [0.5ex]
   \bottomrule
  \end{tabular}
  \label{fig:USAvsWorld}

\end{center}
\end{table}

The dataset of the four United States athletes 
is too small to perform any meaningful statistical analysis, but
the data was expanded to include reaction times for athletes who competed at 
national competitions (many of which were held from May-July of 2022). Once the 
data was collected, each athlete was designated as a cluster and the stage of
competition (national or international) was specified for each competition 
within the cluster (athlete).  We chose to include preliminary rounds in this
section as well as in section~\ref{sec:data2019} in order to increase the size of our
data.  Without data from the preliminary rounds, the number of observations
dropped from 65 to 26 and the number of athletes included in the analysis
decreased from 15 to 9.

@@

\subsubsection{2019 World Track and Field Championships}\label{sec:data2019}
The 2019 World Track and Field Championship data is included in the larger dataset
described in section~\ref{sec:dataworld}, but we can also use it similarly to
how we used national level in section~\ref{sec:datanational}.  We can compare
the times of athletes who participated in the 2019 and 2022 World Track and Field
Championships to see if there were lower times in 2022.  While it is theoretically
possible that athletes got faster between 2019 and 2022, it is important to
remember that these are some of the fastest sprinters on the planet, and thus
improving on elite times is not easy.  Nonetheless, this is a worthy inclusion
to the data because Seiko was the timing company responsible for both events and
because the level of competition is the extremely elite in both cases.

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics{Pooled_Boxplot}
  \caption{The reaction times from 1999 to 2022 for the men's final (top) and
  the men's semifinals and finals (bottom).}
  \label{fig:Boxplots}
\end{figure}

@@

\subsubsection{2022 National Competitions}\label{sec:datanational}
From June 23-26 2022, the United States held its Track and Field Championships 
at Hayward Field in Eugene, Oregon to decide who to send to the World 
Championships being held at the same venue in August. Thus, we can establish a 
baseline for the four United States athletes who competed in at least one round 
of both events: Trey Cunningham, Daniel Roberts, Grant Holloway, and Devon Allen.   
Every athlete reacted faster in all the World Track and Field Championships 
races compared to the United States Track and Field Championships races. The 
dataset of the four United States athletes is too small to perform any 
meaningful statistical analysis, but the data was expanded to include reaction 
times for 11 athletes who competed at national competitions (many of which were 
held from May-July of 2022). This data is difficult to find as it was taken from 
various websites and was at times difficult to interpret as the data if often 
recorded in the language of the country. \of{I don't know how to say this}. Each
athlete was designated to be a cluster and the stage of competition (national or international) was specified for each competition within the cluster (athlete).
Thus, this is subunit level grouping where we assign the treatment: national or
international within each cluster.  Cluster sizes range from three to six, with
one cluster of size three, six clusters of size four, two clusters of size five
and two clusters of size six.  We chose to include preliminary rounds in this
section as well as in section~\ref{sec:data2019} in order to increase the size of our
data.  Without data from the preliminary rounds, the number of observations
dropped from 65 to 26 and the number of athletes included in the analysis
decreased from 15 to 9.

@@

\subsubsection{2019 World Track and Field Championships}\label{sec:data2019}
The 2019 World Track and Field Championship data is included in the larger dataset
described in section~\ref{sec:dataworld}, but we can also use it similarly to
how we used national level in section~\ref{sec:datanational}.  We can compare
the times of athletes who participated in the 2019 and 2022 World Track and Field
Championships to see if there were lower times in 2022.  While it is theoretically
possible that athletes got faster between 2019 and 2022, it is important to
remember that these are some of the fastest sprinters on the planet, and thus
improving on elite times is not easy.  Once again we repeat a similar procedure
as in section~\ref{sec:datanational}; we assign each athlete to be a cluster and
within each cluster assign times to be from either the 2019 World Championships
or the 2022 World Championships.  In this analysis, we look at data from 15
athletes, where cluster size ranges from two to six.   There were two clusters 
of size two, three clusters of size three, five clusters of size four, two 
clusters of size five and three clusters of size six.
